---
title: "Posting Replication Scripts Online"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{posting_replication_scripts_online}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Replication scripts can be posted on a number of wesbites. Below are snippets that can be used to post on a Github repository or posted directly on the Wordpress platform.

# Wordpress site

Below we use the `RWordPress` package developed by Duncan Temple Lang ([here](https://github.com/duncantl/RWordPress)). It allows users to send an already compiled .html file to a Wordpress website as a blog post by entering your credentials and blog post-related fields.

```{r setup, message=FALSE, warning=FALSE, eval = FALSE}
if (!require('RWordPress')) {
  # RWordPress and XMLRPC need to be installed from Github
  devtools::install_github(c("duncantl/XMLRPC", "duncantl/RWordPress"))
}
library(knitr)
library(RWordPress)
library(readr)
```

```{r, eval = FALSE}

# File (include full path if the file is not contained in current directory)
html.file =  "20190717_Replication.html"
text = paste(read_lines(html.file, skip = 18), collapse = "\n")

# Set config options (fill in 'username' and 'password' fields)
options(WordpressLogin = c(username = 'password'),
        WordpressURL = 'http://www.mywebsite.nyc/xmlrpc.php')

# Post content/html code goes in 'description'
# Set 'title' to blog post (in this case paper) title
# Set 'publish = FALSE' to create draft post, 'TRUE' to publish post directly
newPost(
  list(description = text, 
       categories = c("Replication"),
       title = "Replication: Humphreys, Sanchez de la Sierra, van der Windt (2019)"
       ), 
  publish = FALSE)

```

See `?RWordPress` for further documentation on `RWordPress` package functions.

# Github repository

Compiled `.md` files will display nicely once they are uploaded to Github. This can be done by editing the output field in the .Rmd YAML:

```{r, eval = FALSE}
output: rmarkdown::github_document
```

or, alternatively, setting `keep_md = TRUE`.

```{r, eval = FALSE}
output: 
  html_document:
    keep_md: true
```
